### 2009-08-31 latex/paper1/contents.tex
paper1

\section{Complex Networks}

Complex network theory found many scale-free networks

Software dependency networks are scale free. CITE Valverde, Myers

Scale free means ... $N(k) \sim k^{-\gamma}$

@@

Many scale-free models have been proposed. Only a few, though, produce modular
networks.

@@

@@

The approach we chose to test our hypothesis was to build a network classifier:
an algorithm that analyses a network and classifies it as a software network or
as a non-software network. If a classifier is capable of classifying with high
accuracy both software and non-software networks...
it gives a fair approximation apply it on synthetic networks. We expect that
some synthetic networks will be so similar to software networks that they will
be classified as software networks.

@@

We've collected 65 systems written in Java and X networks from many domains,
such as sociology, biology, technology and linguistics.

See Appendix A

@@

We have shown empirically that network models found in the literature can
produce synthetic networks that are similar to the network of dependencies
between classes in object-oriented systems. This result supports the use of
synthetic networks in the evaluation of software modularization algorithms that
operate on class dependency networks.

@@

In a future work, we intend to evaluate with synthetic networks some software
clustering algorithms that were previously studied with real data. We will,
then, be able to compare the results obtained with the two approaches.

>>>>

\section{Networks Theory}

Network theory research studies general properties of many types of networks by
using statistical analysis. In the last decade, it has been found that many
networks arising from sociology, biology, technology and other domains have
remarkable similarities. It has been shown that, in these networks, the number
of vertices connected to k edges, N(k), is proportional to $k^{\-gamma}$, where
$\gamma$ is a positive constant. These networks were called scale-free networks.

Network theory has been applied to software networks and it was shown that they
are also scale-free networks CITE Valverde, Myers.

@@

Many models were proposed to explain the formation of scale-free networks. These
models are simple algorithms that can be proven, either formally or emprically,
to generate networks that are scale-free.

@@

out-neighbors(v) 
module(v)
neighbor-modules(v)

choose event with probabilities (p, q, r)
event 1:
  choose w within V according to f(x) = din + in-degree(x)
  add new vertex v to the module of w
  add edge from v to w
event 2:
  choose w within V according to f(x) = dout + out-degree(x)
  add new vertex v to the module of w
  add edge from w to v
event 3:
  choose v within V according to f(x) = dout + out-degree(x)
  choose case with probabilities (mu, 1 - mu)
  case 1: # out
    choose w within neighbor-modules(v) - neighbors(v) according to f(x) = din + in-degree(x)
    add edge from v to w
  case 2:
    choose w within module(v) - neighbors(v) according to f(x) = din + in-degree(x)
    add edge from v to w
end

@@

The approach we chose to test our hypothesis was to build a network classifier:
an algorithm that analyses a network and classifies it as a software network or
as a non-software network. If a classifier is capable of classifying with high
accuracy both software and non-software networks, then we can apply it to
synthetic networks and see if they are discernable from software networks.
it gives a fair approximation apply it on synthetic networks. We expect that
some synthetic networks will be so similar to software networks that they will
be classified as software networks.

@@

For this experiment we have collected 65 software systems written in the Java
programming language and 66 networks from other domains, such as biology,
sociology and linguistics. Both the software systems and the networks are freely
available on the Internet.

As of this writing, Java is a popular programming language, for which there is
plenty of open source software CITE. Also, there are many dependency extractors
for this language. We have extracted the dependency network for each software
system using a tool called Dependency Finder CITE, for its easy integration with
scripts. Dependency Finder looks for dependencies by means of static analysis of
Java bytecode and outputs the dependency network in a XML file. Although this
network is in a detailed level, showing dependencies between fine-grained
implementation entities such as attributes and methods, we have abstracted it to
a network of dependencies between classes. The network is directed and
non-weighted. The size of the networks range from XXX to YYY.

% JARs?

The networks from other domains were collected in websites of complex network
research groups. The domains include sociology, linguistics, biology and
technology. The size of the networks range from XXX to YYY vertices.

@@

We have shown empirically that network models found in the literature can
produce synthetic networks that are similar to the network of dependencies
between classes in object-oriented systems. This result supports the use of
synthetic networks in the evaluation of software modularization algorithms.
%that operate on class dependency networks.

@@

In a future work, we intend to evaluate with synthetic networks some software
clustering algorithms that were previously studied with real data. We will,
then, be able to compare the results obtained by both approaches.
